02 - Teams reviews

### 2022-06-24 scripts/r/02_teams_reviews.Rmd
✨ - upload reviews to osf components

reviews <- read_csv(list.files("data/peer_review/", full.names = TRUE), skip = 3, col_names = cols[[1]]) %>%
  mutate(
    q6 = case_when(
      Q6 == "deeply flawed and unpublishable." ~ 0,
      Q6 == "publishable with major revision." ~ 1,
      Q6 == "publishable with minor revision." ~ 2,
      Q6 == "publishable as is." ~ 3
    )
  )
```

>>>>

reviews <- read_csv(list.files("data/peer_review/", full.names = TRUE), skip = 3, col_names = cols[[1]]) %>%
  mutate(
    q6 = case_when(
      Q6 == "deeply flawed and unpublishable." ~ 0,
      Q6 == "publishable with major revision." ~ 1,
      Q6 == "publishable with minor revision." ~ 2,
      Q6 == "publishable as is." ~ 3
    )
  ) %>%
  drop_na(Q3) %>%
  filter(Finished == TRUE)
```

```{r analytic-quest}
dir.create("data/peer_review/msa_reviews/", showWarnings = FALSE)

for (team in unique(reviews$Q3)) {
  file_name <- as.character(glue("data/peer_review/msa_reviews/{team}.csv"))

  reviews %>%
    filter(Q3 == team) %>%
    select(-(StartDate:Q2)) %>%
    write_csv(file_name)
}
```
